Paper Analysis

### 2025-04-17 Paper_WriteUp/Paper_Plots.qmd
in process of doing simulated mu_beta plots. Not finished, should probably split it all into different chunks

# #the simulated dataset and corresponding fit to plot
# sim_dataset_num = 3
# 
# #global effects
# facet_labels = as_labeller(c(
#   mu_beta = "mu[beta]",
#   gamma1 = "gamma[1]",
#   gamma2 = "gamma[2]",
#   sigma_1 = "sigma[1]",
#   `tau[1]` = "tau[1]",
#   `tau[2]` = "tau[2]",
#   sigma_g1 = "sigma[g[1]]",
#   sigma_g2 = "sigma[g[2]]"
# ), label_parsed)
# 
# global_plot = sim_fit_list[[sim_dataset_num]]$draws(c("mu_beta", "gamma1", "gamma2", "sigma_1", "tau[1]", "tau[2]", "sigma_g1", "sigma_g2")) |> 
#   as_draws_df() |> 
#   pivot_longer(cols = "mu_beta":"sigma_g2") |> 
#   ggplot(aes(value)) +
#   geom_histogram() +
#    facet_wrap(~name, ncol = 4, scales = "free",
#              labeller = labeller(name = facet_labels)) +
#   labs(x = element_blank(), y = element_blank()) +
#   theme_4col() +
#   scale_x_continuous(breaks = breaks_pretty(n = 2)) 
# global_plot
# 
# 
# #experiential effects
# mod_pars = sim_fit_list[[sim_dataset_num]]$draws() |>
#     as_draws_df() |>
#     select(-any_of(c("lp__", ".chain", ".iteration", ".draw"))) |>
#     pivot_longer(cols = everything()) |>
#     filter(startsWith(name, "beta[2")) |>
#     mutate(id = stringr::str_extract(name, pattern = "\\d+]"),
#            id = stringr::str_replace(id, "\\]", ""), 
#            id = as.numeric(id))
# 
# #order of min to max estiamted betas - makes plot look nicer
# beta_order = mod_pars %>% group_by(id) %>% summarise(mean = mean(value)) %>% arrange(mean) %>% pull(id)
# 
# #true experiential effects
# true_betas = sim_datasets_list[[sim_dataset_num]] %>% 
#   group_by(player_id) %>% 
#   summarise(true_beta = unique(beta)) %>%
#   rename(id = player_id)
# 
# #reordering
# true_betas = true_betas[match(beta_order, true_betas$id),] %>% 
#   mutate(ymin = as.numeric(factor(row_number())) - 0.2,
#          ymax = as.numeric(factor(row_number())) + 0.2)
# 
# #plot
# winner_plot = mod_pars |> 
#   ggplot(aes(y = reorder(id, value, FUN = median), x = value)) +
#   stat_histinterval() +
#   geom_segment(data = true_betas,
#                aes(x = true_beta, xend = true_beta, y = ymin, yend = ymax),
#                color = "orange", linetype = "dashed", linewidth = 2) +
#   labs(x = "Estimated Experiential Effect", y = "Simulated Player ID") +
#   geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
#   theme_single_y()
# winner_plot

@@

@@

#save
ggsave(plot = big_effect_plot, 
       filename = here("Paper_WriteUp", "paper_figures", "fig_sim_3.png"), dpi = 1000,
       height = 6, width = 7)
```

>>>>

#the simulated dataset and corresponding fit to plot
sim_dataset_num = 3

#global effects
facet_labels = as_labeller(c(
  mu_beta = "mu[beta]",
  gamma1 = "gamma[1]",
  gamma2 = "gamma[2]",
  sigma_1 = "sigma[1]",
  `tau[1]` = "tau[1]",
  `tau[2]` = "tau[2]",
  sigma_g1 = "sigma[g[1]]",
  sigma_g2 = "sigma[g[2]]"
), label_parsed)

global_plot = sim_fit_list[[sim_dataset_num]]$draws(c("mu_beta", "gamma1", "gamma2", 
                                                      "sigma_1", "tau[1]", "tau[2]", 
                                                      "sigma_g1", "sigma_g2")) |>
  as_draws_df() |>
  pivot_longer(cols = "mu_beta":"sigma_g2") |>
  ggplot(aes(value)) +
  geom_histogram() +
   facet_wrap(~name, ncol = 4, scales = "free",
             labeller = labeller(name = facet_labels)) +
  labs(x = element_blank(), y = element_blank()) +
  theme_4col() +
  scale_x_continuous(breaks = breaks_pretty(n = 2))
global_plot

# 
# #experiential effects
# mod_pars = sim_fit_list[[sim_dataset_num]]$draws() |>
#     as_draws_df() |>
#     select(-any_of(c("lp__", ".chain", ".iteration", ".draw"))) |>
#     pivot_longer(cols = everything()) |>
#     filter(startsWith(name, "beta[2")) |>
#     mutate(id = stringr::str_extract(name, pattern = "\\d+]"),
#            id = stringr::str_replace(id, "\\]", ""), 
#            id = as.numeric(id))
# 
# #order of min to max estiamted betas - makes plot look nicer
# beta_order = mod_pars %>% group_by(id) %>% summarise(mean = mean(value)) %>% arrange(mean) %>% pull(id)
# 
# #true experiential effects
# true_betas = sim_datasets_list[[sim_dataset_num]] %>% 
#   group_by(player_id) %>% 
#   summarise(true_beta = unique(beta)) %>%
#   rename(id = player_id)
# 
# #reordering
# true_betas = true_betas[match(beta_order, true_betas$id),] %>% 
#   mutate(ymin = as.numeric(factor(row_number())) - 0.2,
#          ymax = as.numeric(factor(row_number())) + 0.2)
# 
# #plot
# winner_plot = mod_pars |> 
#   ggplot(aes(y = reorder(id, value, FUN = median), x = value)) +
#   stat_histinterval() +
#   geom_segment(data = true_betas,
#                aes(x = true_beta, xend = true_beta, y = ymin, yend = ymax),
#                color = "orange", linetype = "dashed", linewidth = 2) +
#   labs(x = "Estimated Experiential Effect", y = "Simulated Player ID") +
#   geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
#   theme_single_y()
# winner_plot

@@

#order of min to max estiamted betas - makes plot look nicer
beta_order = sim_datasets_list[[1]] %>% group_by(player_id) %>% summarise(beta = unique(beta)) %>% arrange(beta) %>% pull(player_id)

@@

#save
ggsave(plot = big_effect_plot, 
       filename = here("Paper_WriteUp", "paper_figures", "fig_sim_3.png"), dpi = 1000,
       height = 6, width = 7)

## same above plot but now mu_beta
mu_beta_draws_list = lapply(sim_fit_list, function(x) {
  x$draws("mu_beta") |>
  as_draws_df()
})

#combing fit results by mu_beta size
small_effect_draws = mu_beta_draws_list[1:3] %>% bind_rows(.id = "column_label") %>% 
  mutate(num_games = case_when(endsWith(column_label, "1") ~ 1000,
                               endsWith(column_label, "2") ~ 5000,
                               endsWith(column_label, "3") ~ 20000),
         num_games = factor(num_games, levels = c("1000", "5000", "20000"))) #make sure the levels are messing up here

med_effect_draws = mu_beta_draws_list[4:6] %>% bind_rows(.id = "column_label") %>% 
  mutate(num_games = case_when(endsWith(column_label, "4") ~ 1000,
                               endsWith(column_label, "5") ~ 5000,
                               endsWith(column_label, "6") ~ 20000),
         num_games = factor(num_games, levels = c("1000", "5000", "20000"))) #make sure the levels are messing up here

big_effect_draws = mu_beta_draws_list[7:9] %>% bind_rows(.id = "column_label") %>% 
  mutate(num_games = case_when(endsWith(column_label, "7") ~ 1000,
                               endsWith(column_label, "8") ~ 5000,
                               endsWith(column_label, "9") ~ 20000),
         num_games = factor(num_games, levels = c("1000", "5000", "20000"))) #make sure the levels are messing up here
